Improving Estimates of the State of Global Fisheries <br> Depends on Better Data

### 2021-06-26 documents/ovando-etal-assessing-global-fisheries.Rmd
merging final version back to main

<!-- data limited are not just messier versions of data rich  -->

<!-- 80% in trouble  -->

<!-- # rishi notes -->

<!-- * more assertive on what the data needs really are -->

<!--   * where to apply globally  -->

<!-- * For places with less coverage, what would we actually recommend there  -->

<!-- * what do we know about catchabiliy -->

<!-- - e.g. 51, fleets became industrial  -->

<!--   - hammer down on that's the issue with the effort  -->

<!--   - how do we translate effort into f bey area -->

<!--   - here's  -->

<!-- https://www.nature.com/natsustain/about/content -->

<!-- # check in call notes -->

<!-- Ray: setting the stage: what we want is a way to assess the status of stocks and see how we're doing relative to SDG. -->

<!-- We need to discuss a sampling strategy: how can we get down to a set of priority stock. A step of expert knowledge to refine what stocks you would focus in on. -->

<!-- Regressions based approach, focusing in effort on stocks -->

<!-- Basically a paragraph laying out that we need to do this, and discussing how we might go about doing that. Equal weight to each stock vs proportional to biomass -->

<!-- add in a bit more to the discussion on guidelines -->

<!-- add in error in the index for the VOI analysis -->

<!-- Apples and apples comparisons between model and design developments. How much is the value of the effort data relative to actually improving the population model. Production model is ill-suited to some of these questions. -->

<!-- fishing effort uncertainty of the effort -->

<!-- how credible is the information -->

<!-- probably don't need to bother with the SAUP -->

<!-- stock assessments -->

<!-- the stock will collapse next year -->

<!-- nansen data -->

<!-- # Publication Requirements -->

<!-- Target Journal: [Nature Sustainability](https://www.nature.com/natsustain/about/content) -->

<!-- 3500 words main text -->

<!-- 50 references (main text) -->

<!-- 3000 words (max) methods -->

<!-- # Significance Statement  {.unnumbered} -->

<!-- <!-- Authors must submit a 120-word-maximum statement about the significance of their research paper written at a level understandable to an undergraduate-educated scientist outside their field of specialty. The primary goal of the Significance Statement is to explain the relevance of the work in broad context to a broad readership. -->

<!-- The health of ocean ecosystems and the well-being of millions of people depend on our ability to accurately estimate the state of marine fish populations. However, these assessments typically require extensive amounts of high-quality data that are not available for large numbers of fisheries that are critical sources of economic and nutritional benefits. Many studies have tried to estimate the state of these unassessed fisheries based solely on the history of catches reported for a fishery, but we show here that these catch-based estimates produce unreliable results. We demonstrate that improving our understanding of global fisheries will depend on redoubled efforts at data collection and capacity building.  -->

@@

Implementation of the United Nations Sustainable Development Goals requires assessments of the global state of fish populations. While we have reliable estimates of stock status for fish populations accounting for approximately half of recent global catch, our knowledge of the state of the majority of the world's 'unassessed' fish stocks remains highly uncertain. Numerous publications have produced estimates of the global status of these unassessed fisheries, but limited quantity and quality of data along with methodological differences have produced counterintuitive and conflicting results. Here, we show that despite numerous efforts, our understanding of the status of global fish stocks remains incomplete, even when new sources of broadly available data are added. Estimates of fish populations based primarily on catch histories alone on average performed 29% better than a random guess. But, on average these methods assigned fisheries to the wrong FAO status category 57% of the time. Effective improvement in estimates of the state of the world's exploited fish populations depends more on expanded collection of new information and efficient use of existing data than development of new modeling methods.

@@

We then fit to the index of abundance per

\begin{equation}
 log(cpue_t) \sim N(f_{pt}(r,K,m,B_0,\pmb{p},\pmb{c}), \sigma_{obs})
(\#eq:cpue)
\end{equation}

@@

```{r cs-plot, fig.cap="RLSADB values of *B/B~MSY~* and *F/F~MSY~* (x-axes) for case study fisheries plotted against estimated values (y-axes) using CMSY [@froese2017], catch heuristics, priors informed by stock-specific Fisheries Management Index (FMI) and swept area ratio (SAR) scores, and an abundance index based on reconstructed effort (Effort) trends assuming a rate of technological increase of 2.6%. Each point is a stock in the RLSADB. Black dashed line shows the 1:1 relationship."}
ex_scatter_plot + 
  theme(strip.text = element_text(size = 8))

ggsave(here("documents","figs","cs-plot.pdf"),ex_scatter_plot)

@@

Looking geographically we found a similar pattern of a rapid decrease in performance for models besides those fit to the RLSADB Index. Across the models, performance was not consistent in space: use of different data performed best or worst for different FAO regions. Models fit to nominal CPUE data substantially overestimate stock status in the Mediterranean, while models based on data using effective CPUE perform better in that region (but worse in others) (Fig.\@ref(fig:mape-map)). We find similarly inconsistent performance for both bias (Fig.\@ref(fig:mpe-map)) and accuracy (Fig.\@ref(fig:acc-map)). Overall, while some data sources performed slightly better than others by some metrics in some places, no models using any non-RLSADB index data were able to capture the overall state or geographic distribution of stock status represented in RLSADB in a consistent manner. Performance in estimating *F/F~MSY~ * was similarly variable and poor, with the exception that the default settings of CMSY performed much more consistently poorly in terms of *F/F~MSY~* than *B/B~MSY~* (due to systemic overestimating of *F/F~MSY~*, see SI).

@@

```{r mpe-map, fig.width=8, fig.height=6, fig.cap="Median percent error (MPE, predicted relative to observed) in most recent *B/B~MSY~* by FAO statistical area from different data sources. Data source panels are ordered in ascending (starting from top left) mean MPE at the FAO region level. RLSADB Index refers to catch and abundance index drawn from RLSADB. Effective CPUE refers to an index of abundance based on reconstructed effort data. Effective CPUE+ uses CPUE along with Fisheries Management Index (FMI) and/or swept area ratio (SAR) data. For both CPUE series 'nominal' assumes a 0% technology creep, for 'effective' a 2.6% technology creep is assumed. FMI uses FMI scores to develop a prior on recent fishing mortality rates, SAR does the same but based on swept area ratio. CMSY uses the methods from Froese et al. 2017 [@froese2017]. Guess assigns a random recent *B/B~MSY~* of 0.4,1, or 1.6. "}
ram_mpe_map_plot

ggsave(here("documents","figs","mpe-map.pdf"), ram_mpe_map_plot, width = 8, height = 6)
```

```{r mape-map, fig.cap = "Median absolute percent error (MAPE) in most recent *B/B~MSY~* by FAO statistical area from different data sources. Data source panels are ordered in descending (starting from top left) mean MAPE at the FAO region level. RLSADB Index refers to catch and abundance index drawn from RLSADB. Effective CPUE refers to an index of abundance based on reconstructed effort data. Effective CPUE+ uses CPUE along with Fisheries Management Index (FMI) and/or swept area ratio (SAR) data. For both CPUE series 'nominal' assumes a 0% technology creep, for 'effective' a 2.6% technology creep is assumed. FMI uses FMI scores to develop a prior on recent fishing mortality rates, SAR does the same but based on swept area ratio. CMSY uses the methods from Froese et al. 2017 [@froese2017]. Guess assigns a random recent *B/B~MSY~* of 0.4,1, or 1.6.",fig.width=8, fig.height=6}
ram_mape_map_plot

ggsave(here("documents","figs","mape-map.pdf"),ram_mape_map_plot, width = 8, height = 6)

@@

```{r acc-map, fig.cap="Mean classification accuracy (assignment to FAO stock status category) by FAO statistical area arising from different data sources. Data source panels are ordered in descending (starting from top left) mean accuracy at the FAO region level RLSADB Index refers to catch and abundance index drawn from RLSADB. Effective CPUE refers to an index of abundance based on reconstructed effort data. Effective CPUE+ uses CPUE along with Fisheries Management Index (FMI) and/or swept area ratio (SAR) data. For both CPUE series 'nominal' assumes a 0% technology creep, for 'effective' a 2.6% technology creep is assumed. FMI uses FMI scores to develop a prior on recent fishing mortality rates, SAR does the same but based on swept area ratio. CMSY uses the methods from Froese et al. 2017 [@froese2017]. Guess assigns a random recent *B/B~MSY~* of 0.4,1, or 1.6.",fig.width=8, fig.height=6}

@@

ggsave(here("documents","figs","acc-map.pdf"),ram_acc_map_plot, width = 8, height = 6)

@@

ggsave(here("documents","figs","voi-plot.pdf"),voi_plot, width = 8, height = 6)

@@

Our claim is that achieving substantial progress in assessing the state of global fisheries will require improved data and capacity building. This claim cannot be definitively proven; it is possible that some yet-to-be discovered model will provide a reliable means of dramatically improving the accuracy of estimates produced by catch-based models using current broadly-available datasets. Basic logic tells us though that such a model would have to depend on strong assumptions, new data, or empirical estimation. Catch is a function of catchability, effort, and biomass, so given just catch we have one equation and three unknowns. Structurally separating out biomass (and subsequently estimating reference points etc.) requires then either data or strong assumptions on these other variables across a sufficiently representative timespan. Alternatively, empirical relationships could be developed linking attributes of catch histories to observed estimates of stock status [@costello2012b;@thorson2012a], or through identifying a structural model for the evolution of fishing mortality in managed and unmanaged fisheries [@thorson2013]. However, these methods require that these empirical relationships both exist and are reliably preserved in fisheries that lack formal assessments. Numerous groups made up of highly skilled scientists have attempted to resolve these fundamental challenges in various ways, but external efforts to validate the performance of these methods have consistently found them to perform generally poorly when applied in bulk [@free2020;@bouch2021;@pons2020]. This is not intended as an indictment of those past efforts, but, we believe, a reflection on the limited amount of broadly applicable predictive power that exists within catch histories alone. Methods tested in those papers have been demonstrated to perform relatively well when given specific data or priors informative to specific fisheries. We revisited this task in this paper, and found that even when augmented with other broadly available datasets, we were unable to produce consistently accurate estimates of stock status around the globe. For these reasons we believe that improvements to our understanding of the state of global unassessed fisheries will come from targeted use of existing but underutilized data, and expanding the collection of high-priority data around the globe, rather than the development of new modeling methods alone.

@@

Funding for this work was provided by the Food and Agriculture Organization of the United Nations (FAO). We thank participants of the FAO "Methods for Global Assessment" workshop held in Rome, Italy February 2019 for helpful feedback on this project. The scientific results and conclusions, as well as any views or opinions expressed herein, are those of the author(s) and do not necessarily reflect those of the FAO, NOAA or the Department of Commerce.

@@

\newpage
# Tables {.unnumbered}

+---------------------------------------------+------------------+--------------------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------+
| Data Source                                 | Short Name       | Data Use                                                                 | Caveats                                                                                                         |
+=============================================+==================+==========================================================================+=================================================================================================================+
| Catch data [@fao2020]                       | catches          | Priors on stock status, scaling of population size, exploitation history | Heuristics or regressions used to translate shape of catch history into priors on stock status                  |
+---------------------------------------------+------------------+--------------------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------+
| Fisheries Management Index [@melnychuk2017] | FMI              | Priors on most recent *F/F~MSY~* values                                    | Priors produced by regression trained on data from RAM Legacy Stock Assessment Database                         |
+---------------------------------------------+------------------+--------------------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------+
| Swept Area Ratio [@amoroso2018]             | SAR              | Priors on most recent *F/F~MSY~* values                                    | Priors produced by regression trained on data from RAM Legacy Stock Assessment Database                         |
+---------------------------------------------+------------------+--------------------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------+
| Reconstructed effort data [@rousseau2019]  | effort           | Combined with catch data to create an index of abundance                 | Total reconstructed effort across all sectors. Assumed rate of technology creep reported in individual sections |
+---------------------------------------------+------------------+--------------------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------+

: (\#tab:data) Data sources included across model fits.

@@

Figure 1: RLSADB values of *B/B~MSY~* and *F/F~MSY~* (x-axes) for case study fisheries plotted against estimated values (y-axes) using CMSY [@froese2017], priors informed by stock-specific Fisheries Management Index (FMI) and swept area ratio (SAR) scores, and an abundance index based on reconstructed effort trends assuming a rate of technological increase of 2.6%. Each point is a stock. Black dashed line shows the 1:1 relationship.

Figure 2: Median percent error (MPE, predicted relative to observed) in most recent *B/B~MSY~* by FAO statistical area from different data sources. RLSADB Index refers to catch and abundance index drawn from RLSADB. Effective CPUE refers to an index of abundance based on reconstructed effort data. Effective CPUE+ uses CPUE along with Fisheries Management Index (FMI) and/or swept area ratio (SAR) data. For both CPUE series 'nominal' assumes a 0% technology creep, for 'effective' a 2.6% technology creep is assumed. FMI uses FMI scores to develop a prior on recent fishing mortality rates, SAR does the same but based on swept area ratio. CMSY uses the methods from Froese et al. 2017 [@froese2017]. Guess assigns a random recent *B/B~MSY~* of 0.4,1, or 1.6. Panels ordered in ascending (starting from top left) mean MPE at the FAO region level.

Figure 3: Median absolute percent error (MAPE) in most recent *B/B~MSY~* by FAO statistical area from different data sources. RLSADB Index refers to catch and abundance index drawn from RLSADB. Effective CPUE refers to an index of abundance based on reconstructed effort data. Effective CPUE+ uses CPUE along with Fisheries Management Index (FMI) and/or swept area ratio (SAR) data. For both CPUE series 'nominal' assumes a 0% technology creep, for 'effective' a 2.6% technology creep is assumed. FMI uses FMI scores to develop a prior on recent fishing mortality rates, SAR does the same but based on swept area ratio. CMSY uses the methods from Froese et al. 2017 [@froese2017]. Guess assigns a random recent *B/B~MSY~* of 0.4,1, or 1.6. Panels ordered in descending (starting from top left) mean MAPE at the FAO region level

Figure 4: Mean classification accuracy (assignment to FAO stock status category) by FAO statistical area arising from different data sources. RLSADB Index refers to catch and abundance index drawn from RLSADB. Effective CPUE refers to an index of abundance based on reconstructed effort data. Effective CPUE+ uses CPUE along with Fisheries Management Index (FMI) and/or swept area ratio (SAR) data. For both CPUE series 'nominal' assumes a 0% technology creep, for 'effective' a 2.6% technology creep is assumed. FMI uses FMI scores to develop a prior on recent fishing mortality rates, SAR does the same but based on swept area ratio. CMSY uses the methods from Froese et al. 2017 [@froese2017]. Guess assigns a random recent *B/B~MSY~* of 0.4,1, or 1.6. Panels ordered in descending (starting from top left) mean accuracy at the FAO region level.

@@

# Supporting Information {.unnumbered}

```{r si, child = 'ovando-etal-assessing-global-fisheries-si.Rmd'}
```

>>>>

@@

Implementation of the United Nations Sustainable Development Goals requires assessments of the global state of fish populations. While we have reliable estimates of stock status for fish populations accounting for approximately half of recent global catch, our knowledge of the state of the majority of the world's 'unassessed' fish stocks remains highly uncertain. Numerous publications have produced estimates of the global status of these unassessed fisheries, but limited quantity and quality of data along with methodological differences have produced counterintuitive and conflicting results. Here, we show that despite numerous efforts, our understanding of the status of global fish stocks remains incomplete, even when new sources of broadly available data are added. Estimates of fish populations based primarily on catch histories on average performed 25% better than a random guess. But, on average these methods assigned fisheries to the wrong FAO status category 57% of the time. Withing these broad summaries the performance of models trained on our tested data sources varied widely across regions. Effective improvement in estimates of the state of the world's exploited fish populations depends more on expanded collection of new information and efficient use of existing data than development of new modeling methods.

@@

We then fit to the index of abundance per Equation 3 and

\begin{equation}
 log(cpue_t) \sim N(B_t, \sigma_{obs})
(\#eq:cpue)
\end{equation}

@@

```{r cs-plot, fig.cap="RLSADB values of *B/B~MSY~* and *F/F~MSY~* (x-axes) for case study fisheries plotted against estimated values (y-axes) using CMSY [@froese2017], catch heuristics, priors informed by stock-specific Fisheries Management Index (FMI) and swept area ratio (SAR) scores, and an abundance index based on reconstructed effort (Effort) trends assuming a rate of technological increase of 2.6%. Each point is a stock in the RLSADB. Black dashed line shows the 1:1 relationship. Text displys root mean squared error (RMSE) of each panel."}
ex_scatter_plot + 
  theme(strip.text = element_text(size = 8))

ggsave(here("documents","figs","cs-plot.png"),ex_scatter_plot, height = 6, width = 6)

@@

Looking geographically we found a similar pattern of a rapid decrease in performance for models besides those fit to the RLSADB Index. Across the models, performance was not consistent in space: use of different data performed best or worst for different FAO regions. Models fit to nominal CPUE data substantially overestimate stock status in the Mediterranean, while models based on data using effective CPUE perform better in that region (but worse in others) (Fig.\@ref(fig:mape-map)). We find similarly inconsistent performance for both bias (Fig.\@ref(fig:mpe-map)) and accuracy (Fig.\@ref(fig:acc-map)). Overall, while some data sources performed slightly better than others by some metrics in some places, no models using any non-RLSADB index data were able to capture the overall state or geographic distribution of stock status represented in RLSADB in a consistent manner. Performance in estimating *F/F~MSY~ * was similarly variable and poor, with the exception that the default settings of CMSY performed much more consistently poorly in terms of *F/F~MSY~* than *B/B~MSY~* (due to systemic overestimation of *F/F~MSY~*, see Supplementary Information [SI]).

@@

```{r mpe-map, fig.width=8, fig.height=6, fig.cap="Median percent error (MPE, predicted relative to observed) in most recent *B/B~MSY~* by FAO statistical area from different data sources. Data source panels are ordered in ascending total bias at the FAO region level. RLSADB Index refers to catch and abundance index drawn from RLSADB. Effective CPUE refers to an index of abundance based on reconstructed effort data. Effective CPUE+ uses CPUE along with Fisheries Management Index (FMI) and/or swept area ratio (SAR) data. For both CPUE series 'nominal' assumes a 0% technology creep, for 'effective' a 2.6% technology creep is assumed. FMI uses FMI scores to develop a prior on recent fishing mortality rates, SAR does the same but based on swept area ratio. CMSY uses the methods from Froese et al. 2017 [@froese2017]. Guess assigns a random recent *B/B~MSY~* of 0.4,1, or 1.6. "}
ram_mpe_map_plot

ggsave(here("documents","figs","mpe-map.png"), ram_mpe_map_plot, width = 8, height = 6)
```

```{r mape-map, fig.cap = "Median absolute percent error (MAPE) in most recent *B/B~MSY~* by FAO statistical area from different data sources. Data source panels are ordered in ascending (starting from top left) mean MAPE at the FAO region level. RLSADB Index refers to catch and abundance index drawn from RLSADB. Effective CPUE refers to an index of abundance based on reconstructed effort data. Effective CPUE+ uses CPUE along with Fisheries Management Index (FMI) and/or swept area ratio (SAR) data. For both CPUE series 'nominal' assumes a 0% technology creep, for 'effective' a 2.6% technology creep is assumed. FMI uses FMI scores to develop a prior on recent fishing mortality rates, SAR does the same but based on swept area ratio. CMSY uses the methods from Froese et al. 2017 [@froese2017]. Guess assigns a random recent *B/B~MSY~* of 0.4,1, or 1.6.",fig.width=8, fig.height=6}
ram_mape_map_plot

ggsave(here("documents","figs","mape-map.png"),ram_mape_map_plot, width = 8, height = 6)

@@

```{r acc-map, fig.cap="Mean classification accuracy (assignment to FAO stock status category) by FAO statistical area arising from different data sources. Data source panels are ordered in descending (starting from top left) mean accuracy at the FAO region level. RLSADB Index refers to catch and abundance index drawn from RLSADB. Effective CPUE refers to an index of abundance based on reconstructed effort data. Effective CPUE+ uses CPUE along with Fisheries Management Index (FMI) and/or swept area ratio (SAR) data. For both CPUE series 'nominal' assumes a 0% technology creep, for 'effective' a 2.6% technology creep is assumed. FMI uses FMI scores to develop a prior on recent fishing mortality rates, SAR does the same but based on swept area ratio. CMSY uses the methods from Froese et al. 2017 [@froese2017]. Guess assigns a random recent *B/B~MSY~* of 0.4,1, or 1.6.",fig.width=8, fig.height=6}

@@

ggsave(here("documents","figs","acc-map.png"),ram_acc_map_plot, width = 8, height = 6)

@@

ggsave(here("documents","figs","voi-plot.png"),voi_plot, width = 8, height = 6)

@@

Our claim is that achieving substantial progress in assessing the state of global fisheries will require improved data and capacity building. This claim cannot be definitively proven; it is possible that some yet-to-be discovered model will provide a reliable means of dramatically improving the accuracy of estimates produced by catch-based models using current broadly-available datasets. Basic logic tells us though that such a model would have to depend on strong assumptions, new data, or empirical estimation. Catch is a function of catchability, effort, and biomass, so given just catch we have one equation and three unknowns. Structurally separating out biomass (and subsequently estimating reference points etc.) requires then either data or strong assumptions on these other variables across a sufficiently representative timespan. Alternatively, empirical relationships could be developed linking attributes of catch histories to observed estimates of stock status [@costello2012b;@thorson2012a], or through identifying a structural model for the evolution of fishing mortality in managed and unmanaged fisheries [@thorson2013]. However, these methods require that these empirical relationships both exist and are reliably preserved in fisheries that lack formal assessments. Numerous groups made up of highly skilled scientists have attempted to resolve these fundamental challenges in various ways, but external efforts to validate the performance of these methods have consistently found them to perform generally poorly when applied in bulk [@free2020;@bouch2021;@pons2020;@sharma2021]. This summary is not intended as a critique of those past efforts, but a reflection on the limited amount of broadly applicable predictive power that exists within catch histories alone. Methods tested in those papers have been demonstrated to perform relatively well when given specific data or priors informative to specific fisheries. We revisited this task in this paper, and found that even when augmented with other broadly available datasets, we were unable to produce consistently accurate estimates of stock status around the globe. For these reasons we believe that improvements to our understanding of the state of global unassessed fisheries will come from targeted use of existing but underutilized data, and expanding the collection of high-priority data around the globe, rather than the development of new modeling methods alone.

@@

Funding for this work was provided by the Food and Agriculture Organization of the United Nations (FAO). We thank participants of the FAO "Methods for Global Assessment" workshop held in Rome, Italy February 2019 for helpful feedback on this project. We also thank A. Hordyk and one anonymous reviewer for their helpful comments. The scientific results and conclusions, as well as any views or opinions expressed herein, are those of the author(s) and do not necessarily reflect those of the FAO, NOAA or the Department of Commerce.

@@

# Tables {.unnumbered}

+---------------------------------------------+------------------+--------------------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------+
| Data Source                                 | Short Name       | Data Use                                                                 | Caveats                                                                                                         |
+=============================================+==================+==========================================================================+=================================================================================================================+
| Catch data [@fao2020]                       | catches          | Priors on stock status, scaling of population size, exploitation history | Heuristics or regressions used to translate shape of catch history into priors on stock status                  |
+---------------------------------------------+------------------+--------------------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------+
| Fisheries Management Index [@melnychuk2017] | FMI              | Priors on most recent *F/F~MSY~* values                                    | Priors produced by regression trained on data from RAM Legacy Stock Assessment Database                         |
+---------------------------------------------+------------------+--------------------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------+
| Swept Area Ratio [@amoroso2018]             | SAR              | Priors on most recent *F/F~MSY~* values                                    | Priors produced by regression trained on data from RAM Legacy Stock Assessment Database                         |
+---------------------------------------------+------------------+--------------------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------+
| Reconstructed effort data [@rousseau2019]  | effort           | Combined with catch data to create an index of abundance                 | Total reconstructed effort across all sectors. Assumed rate of technology creep reported in individual sections |
+---------------------------------------------+------------------+--------------------------------------------------------------------------+-----------------------------------------------------------------------------------------------------------------+
:(\#tab:data) Data sources included across model fits.

@@

Figure 1: RLSADB values of *B/B~MSY~* and *F/F~MSY~* (x-axes) for case study fisheries plotted against estimated values (y-axes) using CMSY [@froese2017], catch heuristics, priors informed by stock-specific Fisheries Management Index (FMI) and swept area ratio (SAR) scores, and an abundance index based on reconstructed effort (Effort) trends assuming a rate of technological increase of 2.6%. Each point is a stock in the RLSADB. Black dashed line shows the 1:1 relationship. Text displys root mean squared error (RMSE) of each panel.

Figure 2: Median percent error (MPE, predicted relative to observed) in most recent *B/B~MSY~* by FAO statistical area from different data sources. Data source panels are ordered in ascending (starting from top left) total bias at the FAO region level. RLSADB Index refers to catch and abundance index drawn from RLSADB. Effective CPUE refers to an index of abundance based on reconstructed effort data. Effective CPUE+ uses CPUE along with Fisheries Management Index (FMI) and/or swept area ratio (SAR) data. For both CPUE series 'nominal' assumes a 0% technology creep, for 'effective' a 2.6% technology creep is assumed. FMI uses FMI scores to develop a prior on recent fishing mortality rates, SAR does the same but based on swept area ratio. CMSY uses the methods from Froese et al. 2017 [@froese2017]. Guess assigns a random recent *B/B~MSY~* of 0.4,1, or 1.6.

Figure 3: Median absolute percent error (MAPE) in most recent *B/B~MSY~* by FAO statistical area from different data sources. Data source panels are ordered in ascending (starting from top left) mean MAPE at the FAO region level. RLSADB Index refers to catch and abundance index drawn from RLSADB. Effective CPUE refers to an index of abundance based on reconstructed effort data. Effective CPUE+ uses CPUE along with Fisheries Management Index (FMI) and/or swept area ratio (SAR) data. For both CPUE series 'nominal' assumes a 0% technology creep, for 'effective' a 2.6% technology creep is assumed. FMI uses FMI scores to develop a prior on recent fishing mortality rates, SAR does the same but based on swept area ratio. CMSY uses the methods from Froese et al. 2017 [@froese2017]. Guess assigns a random recent *B/B~MSY~* of 0.4,1, or 1.6.

Figure 4: Mean classification accuracy (assignment to FAO stock status category) by FAO statistical area arising from different data sources. Data source panels are ordered in descending (starting from top left) mean accuracy at the FAO region level. RLSADB Index refers to catch and abundance index drawn from RLSADB. Effective CPUE refers to an index of abundance based on reconstructed effort data. Effective CPUE+ uses CPUE along with Fisheries Management Index (FMI) and/or swept area ratio (SAR) data. For both CPUE series 'nominal' assumes a 0% technology creep, for 'effective' a 2.6% technology creep is assumed. FMI uses FMI scores to develop a prior on recent fishing mortality rates, SAR does the same but based on swept area ratio. CMSY uses the methods from Froese et al. 2017 [@froese2017]. Guess assigns a random recent *B/B~MSY~* of 0.4,1, or 1.6.

@@

<!-- \newpage -->

<!-- # Supporting Information {.unnumbered} -->

<!-- ```{r si, child = 'ovando-etal-assessing-global-fisheries-si.Rmd'} -->
<!-- ``` -->
